Machine Learning Model for Agricultural Data Applications

### 2021-04-12 chapters/implementation.tex
Implementation completed

\textquote{The garbage in, garbage out (GIGO) is the concept that flawed, or nonsense input data produces nonsense output or garbage}

The pertinent data-sets contained too much extra and irrelevant information. Using Pandas, the data-sets were cleaned, and desired variables were collected into one data-set a tabular frame using the year as the index. A glimpse of the data-frame is shown below:

@@

The repetitive columns constitute noise which isn't required. I drop these to narrow down on the vital data necessary for my task. Two columns are left: \textit{"Year", "Value".} Since the word \textit{"Value"} appears in the different data-sets, it's renamed here as \textit{"Area(Hectares)"} to clearly indicate that this value refers to the measurement of the area.

@@

A similar transformation is performed on the other data-sets. The resulting individual data-sets are: 
\begin{figure}
	\centering
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{fig/areaHectares.png}
		\caption{Area}
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{.24\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{fig/gpv.png}
		\caption{G.P.V}
		\label{fig:sub2}
	\end{subfigure}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{fig/yield.png}
		\caption{Yield}
		\label{fig:sub3}
	\end{subfigure}
	\begin{subfigure}{.24\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{fig/quantityTonnes.png}
		\caption{Quantity}
		\label{fig:sub4}
	\end{subfigure}

@@

\section{Data Loading}
\section{The Neural Networks}
\section{Recurring Neural Network}
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.35\textwidth]{fig/rnn.png}
	\caption{Recurrent Neural Network (RNN)}
	\label{fig:rnn}
\end{figure}
A representative RNN is shown in Figure ~\ref{fig:rnn} showing the hidden layer. The updating of the weight is accomplished as the function of current inputs and previous outputs. Usually, the weights are updated on the basis of output gradients. The weights are only updated, if the underlying gradients are non-zero. As the learning goes on, gradients begin to vanish. At sometimes the gradients are zero, but they should not be. In deep learning literature, this phenomenon is termed as gradient-vanishing problem - GVP \cite{haykin2009neural}. To avoid GVP, two variants of RNNs have been proposed. LSTM (Long-Short Term Memory) recurrent neural network and GRU (Gated-Recurrent Unit).

@@

\section{Deep Learning}

>>>>

\textquote{The garbage in, garbage out (GIGO) is the concept that flawed, or nonsense input data produces nonsense output or garbage.}

The pertinent data-sets contained too much extra and irrelevant information as well some null columns. Using Pandas, the data-sets were cleaned, irrelevant columns were dropped and desired variables were collected into one data-set a tabular frame using the year as the index. A glimpse of the data-frame is shown below:

@@

The repetitive columns constitute noise which isn't required. I dropped these to narrow down on the vital data necessary for my task. Two columns are left: \textit{"Year", "Value".} Since the word \textit{"Value"} appears in the different data-sets, it's renamed here as \textit{"Area(Hectares)"} to clearly indicate that this value refers to the measurement of the area.

@@

A similar transformation is performed on the other data-sets. The resulting individual data-sets are displayed in Fig \ref{fig:heads} : 
\begin{figure}
	\centering
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{fig/areaHectares.png}
		\caption{Area}
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{.24\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{fig/gpv.png}
		\caption{G.P.V}
		\label{fig:sub2}
	\end{subfigure}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{fig/yield.png}
		\caption{Yield}
		\label{fig:sub3}
	\end{subfigure}
	\begin{subfigure}{.24\textwidth}
		\centering
		\includegraphics[width=.4\linewidth]{fig/quantityTonnes.png}
		\caption{Quantity}
		\label{fig:sub4}
	\end{subfigure}

@@

\section{Data Loading}

This is about loading the data to the database. Databases can be divided into either Relational or non-relational databases. Relational database store data in tables and rows. Non relation store data in JSON object. For the purpose of my work, the Python Pandas data-frame was used. This is a two-dimensional data structure where the data is aligned in rows and columns. The data can then be manipulated and vital information extracted.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.35\textwidth]{fig/panda.png}
	\caption{Pandas DataFrame}
	\label{fig:panda}
\end{figure}

\section{Recurring Neural Network}
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.35\textwidth]{fig/rnn.png}
	\caption{Recurrent Neural Network (RNN)}
	\label{fig:rnn}
\end{figure}
A representative RNN is shown in Figure ~\ref{fig:rnn} showing the hidden layer. The updating of the weight is accomplished as the function of current inputs and previous outputs. Usually, the weights are updated on the basis of output gradients. The weights are only updated, if the underlying gradients are non-zero. As the learning goes on, gradients begin to vanish. At sometimes the gradients are zero, but they should not be. In deep learning literature, this phenomenon is termed as gradient-vanishing problem - GVP \cite{haykin2009neural}. To avoid GVP, two variants of RNNs have been proposed. LSTM (Long-Short Term Memory) recurrent neural network and GRU (Gated-Recurrent Unit).

@@
